Weekday sleep, total cholestrol and the modifying effect of age on systolic blood pressure: An analysis of the 2015-2018 non-obese NHANES population

### 2023-12-11 manuscript/paper.Rmd
hi
up
update

Univariate regression analyses were performed on all potentially confounding covariates excluding hypertension. Model 1 was fitted to the data including the exposure variables as well as all potentially confounding covariates from univariate regression analysis. Model 2 was fitted to the same set of covariates including an interaction term between age and total cholesterol levels. Model 3 was fitted to the data including only covariates that had a statistically significant association with SBP in univariate analyses excluding HDL, hemoglobin, diabetes, survey cycle, and alcohol consumption. Model 4 included similar covariates as Model 3 but examined, in addition, all possible two-way interactions between the covariates. Model 5 included the same set of covariates as Model 3 in addition to an interaction term between age and total cholesterol levels.

@@

All models fitted to the data in this investigation were nested and evaluations were based on information criteria including Akaike Information Criteria (AIC) and Bayesian Information Criteria (BIC). Additionally, we also used performance measures including the mean squared error (MSE), r-squared, and adjusted r-squared. The likelihood ratio test (LRT) was used in competing model comparisons testing the null hypothesis that the nested models are equivalent, and the extra parameters in the larger model do not improve the fit significantly, that is, these terms have effect sizes equivalent to 0. \@ref(tab:tabmodel) summarizes the model performance metrics compared for all models implemented in this investigation.

@@

## Model Evaluations

@@

\caption{\label{tab:tabmodel}Summary model performance measures.}
\centering
\begin{tabular}[t]{lrrrrrr}
\toprule
  & df & AIC & BIC & MSE & $R^2$ & Adjusted $R^2$\\
\midrule
Model 1 & 44 & 15888.48 & 16134.41 & 173.17 & 0.36 & 0.34\\
Model 2 & 45 & 15849.26 & 16100.78 & 169.60 & 0.37 & 0.36\\
Model 3 & 39 & 15883.76 & 16101.74 & 173.63 & 0.36 & 0.34\\
Model 4 & 600 & 16156.48 & 19510.09 & 113.00 & 0.58 & 0.40\\
Model 5 & 40 & 15848.93 & 16072.50 & 170.43 & 0.37 & 0.35\\
\addlinespace
Model 6 & 41 & 15888.38 & 16117.55 & 173.69 & 0.36 & 0.34\\
Model 7 & 25 & 15877.41 & 16017.15 & 2657.01 & 0.35 & 0.34\\
\bottomrule
\multicolumn{7}{l}{\textsuperscript{a} df = degrees of freedom}\\
\multicolumn{7}{l}{\textsuperscript{b} AIC = Akaike Information Criteria}\\
\multicolumn{7}{l}{\textsuperscript{c} BIC = Bayesian Information Criteria}\\
\multicolumn{7}{l}{\textsuperscript{d} MSE = Mean Squared Error}\\
\end{tabular}
\end{table}
```
```{r tabmodel, eval=FALSE, echo=FALSE}
## Model performance
tabmodel <- model.checks %>% 
  kable(format = "latex", caption = "Summary model performance measures.", digits = 2, booktabs = TRUE, col.names = c("df", "AIC", "BIC", "MSE", "R^2", "Adjusted R2"), escape = FALSE) %>% 
  add_footnote(label = c("df = degrees of freedom", "AIC = Akaike Information Criteria", "BIC = Bayesian Information Criteria", "MSE = Mean Squared Error"))
tabmodel
```

##

# Conclussion

## Discussion

## Limitations

@@

# References

>>>>

Univariate regression analyses were performed on all potentially
confounding covariates excluding hypertension. Model 1 was fitted to the
data including the exposure variables as well as all potentially
confounding covariates from univariate regression analysis. Model 2 was
fitted to the same set of covariates including an interaction term
between age and total cholesterol levels. Model 3 was fitted to the data
including only covariates that had a statistically significant
association with SBP in univariate analyses excluding HDL, hemoglobin,
diabetes, survey cycle, and alcohol consumption. Model 4 included
similar covariates as Model 3 but examined, in addition, all possible
two-way interactions between the covariates. This model is essentially overfit to the data. Model 5 included the same
set of covariates as Model 3 in addition to an interaction term between
age and total cholesterol levels.

@@

All models fitted to the data in this investigation were nested and
evaluations were based on information criteria including Akaike
Information Criteria (AIC) and Bayesian Information Criteria (BIC). The
BIC is favored over the AIC due to its increasing penalty with larger
sample sizes, resulting in more stringent significance levels [@BIC].
Additionally, we also used performance measures including the mean
squared error (MSE), r-squared, and adjusted r-squared. The likelihood
ratio test (LRT) was used in competing model comparisons testing the
null hypothesis that the nested models are equivalent, and the extra
parameters in the larger model do not improve the fit significantly,
that is, these terms have effect sizes equivalent to 0.
\@ref(tab:tabmodel) summarizes the model performance metrics compared
for all models implemented in this investigation. The final model superiority was based on likelihood ratio tests.

@@

@@

\caption{\label{tab:tabmodel}Summary model performance measures.}
\centering
\begin{tabular}[t]{lrrrrrr}
\toprule
  & df & AIC & BIC & MSE & $R^2$ & Adjusted $R^2$\\
\midrule
Model 1 & 44 & 15888.48 & 16134.41 & 173.17 & 0.36 & 0.34\\
Model 2 & 45 & 15849.26 & 16100.78 & 169.60 & 0.37 & 0.36\\
Model 3 & 39 & 15883.76 & 16101.74 & 173.63 & 0.36 & 0.34\\
Model 4 & 600 & 16156.48 & 19510.09 & 113.00 & 0.58 & 0.40\\
Model 5 & 40 & 15848.93 & 16072.50 & 170.43 & 0.37 & 0.35\\
\addlinespace
Model 6 & 41 & 15888.38 & 16117.55 & 173.69 & 0.36 & 0.34\\
Model 7 & 25 & 15877.41 & 16017.15 & 2657.01 & 0.35 & 0.34\\
\bottomrule
\multicolumn{7}{l}{\textsuperscript{a} df = degrees of freedom}\\
\multicolumn{7}{l}{\textsuperscript{b} AIC = Akaike Information Criteria}\\
\multicolumn{7}{l}{\textsuperscript{c} BIC = Bayesian Information Criteria}\\
\multicolumn{7}{l}{\textsuperscript{d} MSE = Mean Squared Error}\\
\end{tabular}
\end{table}
```

Likelihood ratio tests showed a statistically significant difference between Model 1 and 2 with evidence of in favor of the latter ($\chi^2_{(1)} = 7064; p>0.05$). Model 2 which adjusted for all potentially confounding covariates in \@ref(tab:tabthree) including an interaction between cholestrol level and age was then compared to Model 3 which adjusted for only covariates we found significant in univariate analyses. Results here similarly showed evidence in favor of Model 2 ($\chi^2_{(1)} = 7979; p>0.05$). Comparing Model 2 to Model 3 revealed a non-statistically difference in model fit suggesting that Model 3, even though smaller performed comparably well. Model 3 was thus selected and compared to Model 4, 5, 6, and 7 with evidence based on the LRT favoring its choice as the best model ($p>0.05$). Additional regression diagnostics for Model 3 including residual versus fitted value plots, Q-Q plots for checking the normality of residuals, Cook's distance for outliers, residual and high leverage point plots did not reveal substantial deviations from linear regression assumptions. Model 3 was thus selected as the best model. Reported results are thus based on this model.

```{r tabmodel, eval=FALSE, echo=FALSE}
## Model performance
tabmodel <- model.checks %>% 
  kable(format = "latex", caption = "Summary model performance measures.", digits = 2, booktabs = TRUE, col.names = c("df", "AIC", "BIC", "MSE", "R^2", "Adjusted R2"), escape = FALSE) %>% 
  add_footnote(label = c("df = degrees of freedom", "AIC = Akaike Information Criteria", "BIC = Bayesian Information Criteria", "MSE = Mean Squared Error"))
tabmodel
```

## Discussion and conclusion

### Study limitations

@@

# Refences
